---
title: "Function in R"
author: "Shankar"
date: "2024-02-02"
output: html_document
---

Simple function create and call 
```{r}

studentInfo <- function(){
  name <- "Ram Pandey"
  id <- 10L
  age <- 13
  sprintf("Name of student : %s, Id : %d , Age : %d",name, id,age)
}
studentInfo()

```
Function with parameters and return type

```{r}

stockData <- function(openPrice, closePrice, stockName){
  
  return(paste("Open Price : ", openPrice , "Close Price : ", closePrice, "StockName : ",stockName))
}

stockDetails <- stockData(120, 123, "Apple Inc")
stockDetails

```
Default Parameter Value
If we call the function without an argument, it uses the default value
Use the SPRINTF function to build a string with input parameters.

```{r}

countryDetails <- function(countryName = "Nepal"){
sprintf("Country Name : %s", countryName)  
}

countryDetails("USA")
countryDetails()

```

Lazy Evaluation of Function
In R the functions are executed in a lazy fashion. When we say lazy what it means is if some arguments are missing the function is still executed as long as the execution does not involve those arguments.

```{r}

calcualteArea <- function(l, w, h){
 rectangleArea <- l * w
 return (rectangleArea)
}

print(calcualteArea(2,5))

```
Use the do.call function to allow the user to specify functions.  Functions are specified as a character type.
could be useful if allowing the user to dynamically change graph calculations

```{r}

calcuateItemPrice <- function(price, taxRate){
  totalPrice <- (price * taxRate) + price
  return(totalPrice)
}
resultAfterTax <- do.call(what = "calcuateItemPrice", args = list(130,.89))
resultAfterTax
```

Nested Functions
1. Call a function within another function.

```{r}

governmentTaxes <- function(price, tax){
  toPri <- (price * tax) + price
  return(toPri)
}

govWithLocaltaxes <- function(price, tax){
  locTax <- 1.2
  totalPrice <- (price * tax) + (locTax * price) + price
  return(totalPrice)
}

govWithLocaltaxes(governmentTaxes(100, 0.1), governmentTaxes(100, .90))

```
Write a function within a function.

```{r}

outerFun <- function(num1){
  
  innerFun <- function(num2){
    sumData <- num1+num2
    return(sumData)
  }
  
  return(innerFun)
}

NestedFun <- outerFun(10)
NestedFun(20)

```

R Function Recursion

```{r}

getFact <- function(num){
  
  if(num == 0 || num == 1){
    return(1) 
  }else{
    return(num * getFact(num-1))
  }
}

getFact(5)

```

